Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
dan browne quotes

Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
characteristic of various types of molecules and their interactions. Quantum computing shows promise to eliminate such errors whilst using a
larger number of qubits. However, these factors work against each other. If such a machine can be built, there would be more states and thus
information to manipulate whilst withstanding error. This could revolutionise applications such as pharmaceuticals where cures and treatments
 for complex or incurable diseases such as Cancer, Prion disease and so forth could be engineered. If (or when should I say) this is possible,
  we would have a machine taking on the roles of a chemist, problem solver and designer simultaneously and combined into one entity!

@@

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool these early stage Quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a certainly a promising validation of the
  development of superconducting qubits for scalable quantum hardware".

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
 \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top
 European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent
 part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across
 Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
 the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
 quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
 in garnering serious investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new
 avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.

>>>>

 Although a quantum simulation such as the VQE is almost foolproof it may still not be adequate to calculate exact numerical solutions that are
 characteristic of various types of molecules and their interactions. It’s hard to calculate energies to make such landscapes - Professor of Physics
 Dan Browne at University College London proposed that although VQE has a much simpler quantum circuit it still uses a classical search as part of
 the process to find these molecular energies. “VQE will only work If you have prior knowledge - this helps to refine the search. In the search, you
 need to look in the right place.” He also commented “one could try combining both methods to make a better algorithm”. Could combining PEA and VQE
 conjure up a huge amount of benefits so much that it reduces flaws such as noise and error intolerance?

 Quantum computing shows promise to eliminate such errors whilst using a larger number of qubits. However, these factors work against each other.
 If such a machine can be built, there would be more states and thus information to manipulate whilst withstanding error. This could revolutionise
 applications such as pharmaceuticals where cures and treatments for complex or incurable diseases such as Cancer, Prion disease and so forth could
 be engineered. If (or when should I say) this is possible,  we would have a machine taking on the roles of a chemist, problem solver and designer
  simultaneously and combined into one entity!

@@

 Mikolaj Uryszek, a researcher in the Strongly Correlated Electron Systems group at UCL, commented that "variational techniques in quantum chemistry
 are becoming increasingly prevalent as a useful benchmarking tool to compare these early stage Quantum devices, and this paper by O’Malley et al.
 represents one of the most accurate quantum chemistry simulations using quantum hardware to date, and is a certainly a promising validation of the
  development of superconducting qubits for scalable quantum hardware".

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science
 \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top
 European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent
 part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across
 Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications,
 the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of
 quantum encryption and communication, the myriad opportunities afforded by more efficient and scalable quantum chemistry simulations looms large
 in garnering serious investor interest. The ability to run quantum simulations of the behaviour of atoms and molecules is hoped offer new
 avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.
